---
title: "Exploring the Wharton Data"
output: html_notebook
---
Objectives

1.Proportion of men to women within firm
2.Proportion of white to non-white
3. Within race: we want to look at tenure (group_by industries)


References:

1. Metadata explanation: https://wrds-web.wharton.upenn.edu/wrds/ds/riskmetrics/rmdirectors/index.cfm?navId=245


PART I: Setup, cleaning, and surface-level investigations
```{r}
library(dplyr)
library(datasets)
library(ggplot2)
library(DataExplorer)
```

```{r}
#Let's set the working directory and get the data
setwd('/Users/winsontruong/Dropbox/SEC_ethics')
getwd()

wharton <-read.csv('wharton/select_data.csv')
sp500 <- read.csv('s&p500/sp500.csv')
```

```{r Cleaning}
#Renaming
colnames(sp500)[colnames(sp500)=="Symbol"] <- "ticker"

#Remove Unnecessary Columns
sp500 <- select (sp500,-c(SEC.Filings,HQ.Location))

#Merge
data <- merge(wharton, sp500, by = "ticker")
```

```{r DataExplorer Tools}
#Lets now explore this ungrouped, barely filtered data with DataExplorer
introduce(data)
plot_intro(data)
```


```{r}
#Are we missing anything?
plot_missing(data)
```
This tells me I want to be looking at the last 3 columns: "RT_ID", "Pcnt_Ctrl_VotingPower", "Year_of_termination" so that they don't mess up our data exploration. It seems as if the "Pcnt_Ctrl_VotingPower" is an incredibly sparse column and I'm doubtful of the reliability of the value when it says "NA". 

```{r}
#Lets remove the RT_ID from wharton and year_of_termination, then re-merge
wharton <- select(wharton, -c(RT_ID, Year_of_termination))
data <- merge(wharton, sp500, by = "ticker")
plot_missing(data)
```
Unfortunately, it seems as if the votingpower variable has the most missing data. This is unfortunate because voting power may be a good variable to describe status. Let's drop the column for now and continue to our analysis grouped by industry.

```{r}
wharton <- select(wharton, -c(Pcnt_Ctrl_Votingpower))
data <- merge(wharton, sp500, by = "ticker")
plot_missing(data)
```


```{r}
#Recoding the Female, OWNLESS1
data <- data %>% 
  mutate(female = ifelse(female == "Yes", 1, 0)) %>%
  mutate(OWNLESS1 = ifelse(OWNLESS1 == "Yes", 1, 0))
```

```{r}
create_report(data)
```

## II. Industry Analysis


```{r}
industry_freq <- as.data.frame(table(data$GIC.Sector))
```

```{r}
#Lets compare the number of females CEO in each industry
p < -ggplot(data, aes(x=, y=len)) +
  geom_bar(stat="identity")
p
```


